---
title: "Legionnaire's Outbreaks"
author: "Holly Kessler"
date: "June 3, 2016"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The coordinates of the Legionnaire's Disease outbreaks will be used to gather weather data from surrounding stations. The averages of the data will be taken and outputted into a graph containing data from the last 10 years before the outbreak. 

First I downloaded the packages needed including rnoaa from github.

```{r, eval=FALSE}
install_github("ropenscilabs/rnoaa")
```
```{r, message=FALSE}
library(devtools)
library(rnoaa)
library(ggmap)
library(countyweather)
library(plyr)
library(dplyr)
library(tidyr)
library(weathermetrics)
library(ggplot2)

```

I created a data frame including the locations of each outbreak and information relating to them. I found the coordinates at http://maps.cga.harvard.edu/gpf/ and crossed checked them with Google coordinates. 

```{r,echo=FALSE}

outbreak_loc <- data.frame("id" = c("portugal","pittsburgh","quebec",
                                  "stoke-on-trent","edinburgh","miyazaki","pas-de-calais",
                                  "pamplona","rapid city","christchurch","sarpsborg",
                                  "barrow-in-furness","murcia","melbourne","bovenkarspel",
                                  "london","stafford","philadelphia"),
                           "latitude" = c(38.96, 40.43, 46.85, 53.02, 55.94,
                                          31.89, 50.51, 42.81, 44.06, -43.51,
                                          59.28, 54.10, 37.98, -37.86, 52.7,
                                          51.52, 52.80, 40.00),
                           "longitude" = c(-8.99, -79.98, -71.34, -2.15, -3.20,
                                           131.34, 2.37, -1.65, -103.22,
                                           172.59, 11.08, -3.22, -1.12,
                                           145.07, 5.24, -0.10, -2.10, -75.11),
                           "year_min" = c(2004, 2003, 2002, 2002, 2002, 1992, 
                                          1993, 1996, 1995, 1995, 1995, 1992, 
                                          1991, 1990, 1989, 1979, 1975, 1966),
                           "year_max" = c(2014, 2013, 2012, 2012, 2012, 2002,
                                          2003, 2006, 2005, 2005, 2005, 2002,
                                          2001, 2000, 1999, 1989, 1985, 1976))
outbreak_loc

```

The next function will download information from all of the stations. It only needs to be downloaded once per session. It will take a couple minutes to download

```{r}
station_data <- ghcnd_stations()[[1]]
```

I created a loop to get a list of the stations within 30 km of the location.
```{r}
city_names <- c("portugal","pittsburgh","quebec",
                  "stoke-on-trent","edinburgh","miyazaki","pas-de-calais",
                  "pamplona","rapid city","christchurch","sarpsborg",
                  "barrow-in-furness","murcia","melbourne","bovenkarspel",
                  "london","stafford","philadelphia")

df <- list()
for(i in 1:length(city_names))
            {
              df[i] <- (meteo_nearby_stations(lat_lon_df = outbreak_loc[i,],
                                  station_data = station_data,
                                  var = c("PRCP","TAVG","TMAX","TMIN",
                                          "AWND","MDPR"),
                                  year_min = outbreak_loc[i, "year_min"],
                                  year_max = outbreak_loc[i, "year_max"],
                                  radius = 30))
            }

names(df) <- city_names
stations <- df
stations
```


Using the countyweather codes I can evaluate the averaged weather data for one of the outbreak regions and output it into a plot. 

When pulling the monitor data it is important to put the date min and max because it will evaluated all the data the monitor has and will take a very long time. 

```{r, eval=FALSE}
meteo_df <- meteo_pull_monitors(monitors = stations$quebec$id,
                                keep_flags = FALSE,
                                date_min = "2002-01-01",
                                date_max = "2012-12-31",
                                var = "all")

coverage_df <- meteo_coverage(meteo_df, verbose = FALSE)

filtered <- filter_coverage(coverage_df, 0.90)
good_monitors <- unique(filtered$id)

filtered_data <- filter(meteo_df, id %in% good_monitors)

averaged <- ave_weather(filtered_data)

ggplot(averaged, aes(x=date, y=prcp)) + 
  ylab("PRCP (10ths of mm)") + xlab("Year") + ggtitle("Quebec PRCP") +
  geom_line() + theme_minimal()
```

Below are all the plots using the above code. The cities lacking plots do not have any stations within 30km of the outbreak location.

```{r, echo=FALSE}
###PORTUGAL-NULL###

###PITTSBURGH###
meteo_df <- meteo_pull_monitors(monitors = stations$pittsburgh$id,
                                keep_flags = FALSE,
                                date_min = "2003-01-01",
                                date_max = "2013-12-31",
                                var = "all")
coverage_df <- meteo_coverage(meteo_df, verbose = FALSE)
filtered <- filter_coverage(coverage_df, 0.90)
good_monitors <- unique(filtered$id)
filtered_data <- filter(meteo_df, id %in% good_monitors)
averaged <- ave_weather(filtered_data)

ggplot(averaged, aes(x=date, y=prcp)) + 
  ylab("Precipitation (mm)") + xlab("Year") + ggtitle("Pittsburgh Precipitation") +
  geom_line() + theme_minimal()
ggplot(averaged, aes(x=date, y=snow)) + 
  ylab("Snowfall (mm)") + xlab("Year") + ggtitle("Pittsburgh Snowfall") +
  geom_line() + theme_minimal()
ggplot(averaged, aes(x=date, y=snwd)) + 
  ylab("Snow Depth (mm)") + xlab("Year") + ggtitle("Pittsburgh Snow Depth") +
  geom_line() + theme_minimal()
ggplot(averaged, aes(x=date, y=tmax)) + 
  ylab(" Max Temperature (C)") + xlab("Year") + ggtitle("Pittsburgh Max Temperature") +
  geom_line() + theme_minimal()
ggplot(averaged, aes(x=date, y=tmin)) + 
  ylab(" Min Temperature (C)") + xlab("Year") + ggtitle("Pittsburgh Min Temperature") +
  geom_line() + theme_minimal()

###QUEBEC###
meteo_df <- meteo_pull_monitors(monitors = stations$quebec$id,
                                keep_flags = FALSE,
                                date_min = "2002-01-01",
                                date_max = "2012-12-31",
                                var = "all")
coverage_df <- meteo_coverage(meteo_df, verbose = FALSE)
filtered <- filter_coverage(coverage_df, 0.90)
good_monitors <- unique(filtered$id)
filtered_data <- filter(meteo_df, id %in% good_monitors)
averaged <- ave_weather(filtered_data)

ggplot(averaged, aes(x=date, y=prcp)) + 
  ylab("Precipitation (mm)") + xlab("Year") + ggtitle("Quebec Precipitation") +
  geom_line() + theme_minimal()
ggplot(averaged, aes(x=date, y=snow)) + 
  ylab("Snowfall (mm)") + xlab("Year") + ggtitle("Quebec Snowfall") +
  geom_line() + theme_minimal()
ggplot(averaged, aes(x=date, y=snwd)) + 
  ylab("Snow Depth (mm)") + xlab("Year") + ggtitle("Quebec Snow Depth") +
  geom_line() + theme_minimal()
ggplot(averaged, aes(x=date, y=tmax)) + 
  ylab(" Max Temperature (C)") + xlab("Year") + ggtitle("Quebec Max Temperature") +
  geom_line() + theme_minimal()
ggplot(averaged, aes(x=date, y=tmin)) + 
  ylab(" Min Temperature (C)") + xlab("Year") + ggtitle("Quebec Min Temperature") +
  geom_line() + theme_minimal()

###STOKE-ON-TRENT=NULL###

###EDINBURGH=NULL###

###MIYAZAKI###
meteo_df <- meteo_pull_monitors(monitors = stations$miyazaki$id,
                                keep_flags = FALSE,
                                date_min = "1992-01-01",
                                date_max = "2002-12-31",
                                var = "all")
coverage_df <- meteo_coverage(meteo_df, verbose = FALSE)
filtered <- filter_coverage(coverage_df, 0.90)
good_monitors <- unique(filtered$id)
filtered_data <- filter(meteo_df, id %in% good_monitors)
averaged <- ave_weather(filtered_data)

ggplot(averaged, aes(x=date, y=prcp)) + 
  ylab("Precipitation (mm)") + xlab("Year") + ggtitle("Miyazaki Precipitation") +
  geom_line() + theme_minimal()
ggplot(averaged, aes(x=date, y=tavg)) + 
  ylab("Average Temperature (C)") + xlab("Year") + ggtitle("Miyazaki Average Temperature") +
  geom_line() + theme_minimal()
ggplot(averaged, aes(x=date, y=tmax)) + 
  ylab(" Max Temperature (C)") + xlab("Year") + ggtitle("Miyazaki Max Temperature") +
  geom_line() + theme_minimal()
ggplot(averaged, aes(x=date, y=tmin)) + 
  ylab(" Min Temperature (C)") + xlab("Year") + ggtitle("Miyazaki Min Temperature") +
  geom_line() + theme_minimal()

###PAS-DE-CALAIS=NULL###

###PAMPLONA###
meteo_df <- meteo_pull_monitors(monitors = stations$pamplona$id,
                                keep_flags = FALSE,
                                date_min = "1996-01-01",
                                date_max = "2006-12-31",
                                var = "all")
coverage_df <- meteo_coverage(meteo_df, verbose = FALSE)
filtered <- filter_coverage(coverage_df, 0.90)
good_monitors <- unique(filtered$id)
filtered_data <- filter(meteo_df, id %in% good_monitors)
averaged <- ave_weather(filtered_data)

ggplot(averaged, aes(x=date, y=prcp)) + 
  ylab("Precipitation (mm)") + xlab("Year") + ggtitle("Pamplona Precipitation") +
  geom_line() + theme_minimal()
ggplot(averaged, aes(x=date, y=tavg)) + 
  ylab("Average Temperature (C)") + xlab("Year") + ggtitle("Pamplona Average Temperature") +
  geom_line() + theme_minimal()
ggplot(averaged, aes(x=date, y=snwd)) + 
  ylab("Snow Depth (mm)") + xlab("Year") + ggtitle("Pamplona Snow Depth") +
  geom_line() + theme_minimal()
ggplot(averaged, aes(x=date, y=tmax)) + 
  ylab(" Max Temperature (C)") + xlab("Year") + ggtitle("Pamplona Max Temperature") +
  geom_line() + theme_minimal()
ggplot(averaged, aes(x=date, y=tmin)) + 
  ylab(" Min Temperature (C)") + xlab("Year") + ggtitle("Pamplona Min Temperature") +
  geom_line() + theme_minimal()

###RAPID CITY###
meteo_df <- meteo_pull_monitors(monitors = stations$`rapid city`$id,
                                keep_flags = FALSE,
                                date_min = "1995-01-01",
                                date_max = "2005-12-31",
                                var = "all")
coverage_df <- meteo_coverage(meteo_df, verbose = FALSE)
filtered <- filter_coverage(coverage_df, 0.90)
good_monitors <- unique(filtered$id)
filtered_data <- filter(meteo_df, id %in% good_monitors)
averaged <- ave_weather(filtered_data)

ggplot(averaged, aes(x=date, y=prcp)) + 
  ylab("Precipitation (mm)") + xlab("Year") + ggtitle("Rapid City Precipitation") +
  geom_line() + theme_minimal()
ggplot(averaged, aes(x=date, y=snow)) + 
  ylab("Snowfall (mm)") + xlab("Year") + ggtitle("Rapid City Snowfall") +
  geom_line() + theme_minimal()
ggplot(averaged, aes(x=date, y=snwd)) + 
  ylab("Snow Depth (mm)") + xlab("Year") + ggtitle("Rapid City Snow Depth") +
  geom_line() + theme_minimal()
ggplot(averaged, aes(x=date, y=tmax)) + 
  ylab(" Max Temperature (C)") + xlab("Year") + ggtitle("Rapid City Max Temperature") +
  geom_line() + theme_minimal()
ggplot(averaged, aes(x=date, y=tmin)) + 
  ylab(" Min Temperature (C)") + xlab("Year") + ggtitle("Rapid City Min Temperature") +
  geom_line() + theme_minimal()
ggplot(averaged, aes(x=date, y=tavg)) + 
  ylab("Average Temperature (C)") + xlab("Year") + ggtitle("Rapid City Average Temperature") +
  geom_line() + theme_minimal()

###CHRISTCHURCH###
meteo_df <- meteo_pull_monitors(monitors = stations$christchurch$id,
                                keep_flags = FALSE,
                                date_min = "1995-01-01",
                                date_max = "2005-12-31",
                                var = "all")
coverage_df <- meteo_coverage(meteo_df, verbose = FALSE)
filtered <- filter_coverage(coverage_df, 0.90)
good_monitors <- unique(filtered$id)
filtered_data <- filter(meteo_df, id %in% good_monitors)
averaged <- ave_weather(filtered_data)

ggplot(averaged, aes(x=date, y=prcp)) + 
  ylab("Precipitation (mm)") + xlab("Year") + ggtitle("Christchurch Precipitation") +
  geom_line() + theme_minimal()
ggplot(averaged, aes(x=date, y=tavg)) + 
  ylab("Average Temperature (C)") + xlab("Year") + ggtitle("Christchurch Average Temperature") +
  geom_line() + theme_minimal()
ggplot(averaged, aes(x=date, y=snwd)) + 
  ylab("Snow Depth (mm)") + xlab("Year") + ggtitle("Christchurch Snow Depth") +
  geom_line() + theme_minimal()
ggplot(averaged, aes(x=date, y=tmax)) + 
  ylab(" Max Temperature (C)") + xlab("Year") + ggtitle("Christchurch Max Temperature") +
  geom_line() + theme_minimal()
ggplot(averaged, aes(x=date, y=tmin)) + 
  ylab(" Min Temperature (C)") + xlab("Year") + ggtitle("Christchurch Min Temperature") +
  geom_line() + theme_minimal()

###SARPSBORG###
meteo_df <- meteo_pull_monitors(monitors = stations$sarpsborg$id,
                                keep_flags = FALSE,
                                date_min = "1995-01-01",
                                date_max = "2005-12-31",
                                var = "all")
coverage_df <- meteo_coverage(meteo_df, verbose = FALSE)
filtered <- filter_coverage(coverage_df, 0.90)
good_monitors <- unique(filtered$id)
filtered_data <- filter(meteo_df, id %in% good_monitors)
averaged <- ave_weather(filtered_data)

ggplot(averaged, aes(x=date, y=prcp)) + 
  ylab("Precipitation (mm)") + xlab("Year") + ggtitle("Sarpsborg Precipitation") +
  geom_line() + theme_minimal()
ggplot(averaged, aes(x=date, y=snwd)) + 
  ylab("Snow Depth (mm)") + xlab("Year") + ggtitle("Sarpsborg Snow Depth") +
  geom_line() + theme_minimal()
ggplot(averaged, aes(x=date, y=tmax)) + 
  ylab(" Max Temperature (C)") + xlab("Year") + ggtitle("Sarpsborg Max Temperature") +
  geom_line() + theme_minimal()
ggplot(averaged, aes(x=date, y=tmin)) + 
  ylab(" Min Temperature (C)") + xlab("Year") + ggtitle("Sarpsborg Min Temperature") +
  geom_line() + theme_minimal()

###BARROW-IN-FURNESS=NULL###

###MURCIA###
meteo_df <- meteo_pull_monitors(monitors = stations$murcia$id,
                                keep_flags = FALSE,
                                date_min = "1991-01-01",
                                date_max = "2001-12-31",
                                var = "all")
coverage_df <- meteo_coverage(meteo_df, verbose = FALSE)
filtered <- filter_coverage(coverage_df, 0.90)
good_monitors <- unique(filtered$id)
filtered_data <- filter(meteo_df, id %in% good_monitors)
averaged <- ave_weather(filtered_data)

ggplot(averaged, aes(x=date, y=prcp)) + 
  ylab("Precipitation (mm)") + xlab("Year") + ggtitle("Murcia Precipitation") +
  geom_line() + theme_minimal()
ggplot(averaged, aes(x=date, y=tavg)) + 
  ylab("Average Temperature (C)") + xlab("Year") + ggtitle("Murcia Average Temperature") +
  geom_line() + theme_minimal()
ggplot(averaged, aes(x=date, y=snwd)) + 
  ylab("Snow Depth (mm)") + xlab("Year") + ggtitle("Murcia Snow Depth") +
  geom_line() + theme_minimal()
ggplot(averaged, aes(x=date, y=tmax)) + 
  ylab(" Max Temperature (C)") + xlab("Year") + ggtitle("Murcia Max Temperature") +
  geom_line() + theme_minimal()
ggplot(averaged, aes(x=date, y=tmin)) + 
  ylab(" Min Temperature (C)") + xlab("Year") + ggtitle("Murcia Min Temperature") +
  geom_line() + theme_minimal()

###MELBOURNE###
meteo_df <- meteo_pull_monitors(monitors = stations$melbourne$id,
                                keep_flags = FALSE,
                                date_min = "1990-01-01",
                                date_max = "2000-12-31",
                                var = "all")
coverage_df <- meteo_coverage(meteo_df, verbose = FALSE)
filtered <- filter_coverage(coverage_df, 0.90)
good_monitors <- unique(filtered$id)
filtered_data <- filter(meteo_df, id %in% good_monitors)
averaged <- ave_weather(filtered_data)

ggplot(averaged, aes(x=date, y=prcp)) + 
  ylab("Precipitation (mm)") + xlab("Year") + ggtitle("Melbourne Precipitation") +
  geom_line() + theme_minimal()
ggplot(averaged, aes(x=date, y=tavg)) + 
  ylab("Average Temperature (C)") + xlab("Year") + ggtitle("Melbourne Average Temperature") +
  geom_line() + theme_minimal()
ggplot(averaged, aes(x=date, y=snwd)) + 
  ylab("Snow Depth (mm)") + xlab("Year") + ggtitle("Melbourne Snow Depth") +
  geom_line() + theme_minimal()
ggplot(averaged, aes(x=date, y=tmax)) + 
  ylab(" Max Temperature (C)") + xlab("Year") + ggtitle("Melbourne Max Temperature") +
  geom_line() + theme_minimal()
ggplot(averaged, aes(x=date, y=tmin)) + 
  ylab(" Min Temperature (C)") + xlab("Year") + ggtitle("Melbourne Min Temperature") +
  geom_line() + theme_minimal()

###BOVENKARSPEL###
meteo_df <- meteo_pull_monitors(monitors = stations$bovenkarspel$id,
                                keep_flags = FALSE,
                                date_min = "1989-01-01",
                                date_max = "1999-12-31",
                                var = "all")
coverage_df <- meteo_coverage(meteo_df, verbose = FALSE)
filtered <- filter_coverage(coverage_df, 0.90)
good_monitors <- unique(filtered$id)
filtered_data <- filter(meteo_df, id %in% good_monitors)
averaged <- ave_weather(filtered_data)

ggplot(averaged, aes(x=date, y=prcp)) + 
  ylab("Precipitation (mm)") + xlab("Year") + ggtitle("Bovenkarspel Precipitation") +
  geom_line() + theme_minimal()
ggplot(averaged, aes(x=date, y=snwd)) + 
  ylab("Snow Depth (mm)") + xlab("Year") + ggtitle("Bovenkarspel Snow Depth") +
  geom_line() + theme_minimal()
ggplot(averaged, aes(x=date, y=tmax)) + 
  ylab(" Max Temperature (C)") + xlab("Year") + ggtitle("Bovenkarspel Max Temperature") +
  geom_line() + theme_minimal()
ggplot(averaged, aes(x=date, y=tmin)) + 
  ylab(" Min Temperature (C)") + xlab("Year") + ggtitle("Bovenkarspel Min Temperature") +
  geom_line() + theme_minimal()

###LONDON###
meteo_df <- meteo_pull_monitors(monitors = stations$london$id,
                                keep_flags = FALSE,
                                date_min = "1979-01-01",
                                date_max = "1989-12-31",
                                var = "all")
coverage_df <- meteo_coverage(meteo_df, verbose = FALSE)
filtered <- filter_coverage(coverage_df, 0.90)
good_monitors <- unique(filtered$id)
filtered_data <- filter(meteo_df, id %in% good_monitors)
averaged <- ave_weather(filtered_data)

ggplot(averaged, aes(x=date, y=prcp)) + 
  ylab("Precipitation (mm)") + xlab("Year") + ggtitle("London Precipitation") +
  geom_line() + theme_minimal()
ggplot(averaged, aes(x=date, y=tavg)) + 
  ylab("Average Temperature (C)") + xlab("Year") + ggtitle("London Average Temperature") +
  geom_line() + theme_minimal()
ggplot(averaged, aes(x=date, y=snwd)) + 
  ylab("Snow Depth (mm)") + xlab("Year") + ggtitle("London Snow Depth") +
  geom_line() + theme_minimal()
ggplot(averaged, aes(x=date, y=tmax)) + 
  ylab(" Max Temperature (C)") + xlab("Year") + ggtitle("London Max Temperature") +
  geom_line() + theme_minimal()
ggplot(averaged, aes(x=date, y=tmin)) + 
  ylab(" Min Temperature (C)") + xlab("Year") + ggtitle("London Min Temperature") +
  geom_line() + theme_minimal()

###STAFFORD=NULL###

###PHILADELPHIA###
meteo_df <- meteo_pull_monitors(monitors = stations$philadelphia$id,
                                keep_flags = FALSE,
                                date_min = "1966-01-01",
                                date_max = "1976-12-31",
                                var = "all")
coverage_df <- meteo_coverage(meteo_df, verbose = FALSE)
filtered <- filter_coverage(coverage_df, 0.90)
good_monitors <- unique(filtered$id)
filtered_data <- filter(meteo_df, id %in% good_monitors)
averaged <- ave_weather(filtered_data)

ggplot(averaged, aes(x=date, y=prcp)) + 
  ylab("Precipitation (mm)") + xlab("Year") + ggtitle("Philadelphia Precipitation") +
  geom_line() + theme_minimal()
ggplot(averaged, aes(x=date, y=snow)) + 
  ylab("Snowfall (mm)") + xlab("Year") + ggtitle("Philadelphia Snowfall") +
  geom_line() + theme_minimal()
ggplot(averaged, aes(x=date, y=snwd)) + 
  ylab("Snow Depth (mm)") + xlab("Year") + ggtitle("Philadelphia Snow Depth") +
  geom_line() + theme_minimal()
ggplot(averaged, aes(x=date, y=tmax)) + 
  ylab(" Max Temperature (C)") + xlab("Year") + ggtitle("Philadelphia Max Temperature") +
  geom_line() + theme_minimal()
ggplot(averaged, aes(x=date, y=tmin)) + 
  ylab(" Min Temperature (C)") + xlab("Year") + ggtitle("Philadelphia Min Temperature") +
  geom_line() + theme_minimal()
```



